\thispagestyle{empty}

\singlespacing
\begin{center}
	\textbf{ABSTRACT}
\end{center}

\noindent Understanding the behavior of intense rainfall in a region through the rainfall Intensity-Duration-Frequency equation is an important step in the development of projects that involve the analysis and control of pluviometric waters. The calculations that lead to the equation mentioned involve the understanding of the relationship between intensity, duration and frequency, as well as calculations that go through treatment of historical data series, optimization methods, probabilistic distributions, and statistical tests of adherence, trend and accuracy. Due to the complexity that exists in the understanding and determination of these equations, corresponding to the extensive probabilistic calculations and analyses, the present work proposed to develop a computational tool with an open source graphical interface. It allows engineers and scholars to calculate the equation for chosen regions from their own databases, or to study the algorithms that drive the entire calculation process.

\ \

\noindent \textbf{Keywords:} palavra 1; palavra 2; palavra 3; palavra 4; palavra 5. (Devem ser grafadas com as iniciais em letra minúscula, com exceção dos substantivos próprios e nomes científicos. As palavras devem ser separadas por ponto e vírgula e finalizadas por ponto). Evite repetir palavras já constantes do título da pesquisa. A ideia é que as palavras-chave tragam informações adicionais da sua pesquisa.
\newpage
